An agent-based model for modal shift in public transport

### 2021-07-23 paper.tex
camera_ready

\bibliographystyle{elsarticle-harv}
\bibliography{biblio.bib}

>>>>

%\bibliographystyle{elsarticle-harv}
%\bibliography{biblio.bib}

\begin{thebibliography}{21}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\href}[2]{#2}
\providecommand{\path}[1]{#1}
\providecommand{\DOIprefix}{doi:}
\providecommand{\ArXivprefix}{arXiv:}
\providecommand{\URLprefix}{URL: }
\providecommand{\Pubmedprefix}{pmid:}
\providecommand{\doi}[1]{\href{http://dx.doi.org/#1}{\path{#1}}}
\providecommand{\Pubmed}[1]{\href{pmid:#1}{\path{#1}}}
\providecommand{\bibinfo}[2]{#2}
\ifx\xfnm\relax \def\xfnm[#1]{\unskip,\space#1}\fi
%Type = Article
\bibitem[{Ambra et~al.(2019)Ambra, Caris and Macharis}]{ambra2019should}
\bibinfo{author}{Ambra, T.}, \bibinfo{author}{Caris, A.},
  \bibinfo{author}{Macharis, C.}, \bibinfo{year}{2019}.
\newblock \bibinfo{title}{Should i stay or should i go? assessing intermodal
  and synchromodal resilience from a decentralized perspective}.
\newblock \bibinfo{journal}{Sustainability} \bibinfo{volume}{11},
  \bibinfo{pages}{1765}.
%Type = Article
\bibitem[{Baindur and Viegas(2011)}]{baindur2011agent}
\bibinfo{author}{Baindur, D.}, \bibinfo{author}{Viegas, J.M.},
  \bibinfo{year}{2011}.
\newblock \bibinfo{title}{An agent based model concept for assessing modal
  share in inter-regional freight transport markets}.
\newblock \bibinfo{journal}{Journal of Transport Geography}
  \bibinfo{volume}{19}, \bibinfo{pages}{1093--1105}.
%Type = Techreport
\bibitem[{Bliemer and Rose(2009)}]{bliemer2009efficiency}
\bibinfo{author}{Bliemer, M.C.}, \bibinfo{author}{Rose, J.M.},
  \bibinfo{year}{2009}.
\newblock \bibinfo{title}{Efficiency and sample size requirements for stated
  choice experiments}.
\newblock \bibinfo{type}{Technical Report}.
%Type = Phdthesis
\bibitem[{Brisbois(2010)}]{brisbois2010processus}
\bibinfo{author}{Brisbois, X.}, \bibinfo{year}{2010}.
\newblock \bibinfo{title}{Le processus de d{\'e}cision dans le choix modal:
  importance des d{\'e}terminants individuels, symboliques et cognitifs}.
\newblock Ph.D. thesis. Universit{\'e} Pierre Mend{\`e}s-France-Grenoble II.
%Type = Article
\bibitem[{Cabannes et~al.(2017)Cabannes, Vincentelli, Sundt, Signargout,
  Porter, Fighiera, Ugirumurera and Bayen}]{cabannes2017impact}
\bibinfo{author}{Cabannes, T.}, \bibinfo{author}{Vincentelli, M.A.S.},
  \bibinfo{author}{Sundt, A.}, \bibinfo{author}{Signargout, H.},
  \bibinfo{author}{Porter, E.}, \bibinfo{author}{Fighiera, V.},
  \bibinfo{author}{Ugirumurera, J.}, \bibinfo{author}{Bayen, A.M.},
  \bibinfo{year}{2017}.
\newblock \bibinfo{title}{The impact of gps-enabled shortest path routing on
  mobility: a game theoretic approach 2}.
\newblock \bibinfo{journal}{University of California, Berkeley} .
%Type = Article
\bibitem[{Chatterjee et~al.(2002)Chatterjee, Hounsell, Firmin and
  Bonsall}]{chatterjee2002driver}
\bibinfo{author}{Chatterjee, K.}, \bibinfo{author}{Hounsell, N.},
  \bibinfo{author}{Firmin, P.}, \bibinfo{author}{Bonsall, P.},
  \bibinfo{year}{2002}.
\newblock \bibinfo{title}{Driver response to variable message sign information
  in london}.
\newblock \bibinfo{journal}{Transportation research part C: Emerging
  technologies} \bibinfo{volume}{10}, \bibinfo{pages}{149--169}.
%Type = Article
\bibitem[{Chorus et~al.(2006)Chorus, Molin and van Wee}]{chorus2006travel}
\bibinfo{author}{Chorus, C.G.}, \bibinfo{author}{Molin, E.J.},
  \bibinfo{author}{van Wee, B.}, \bibinfo{year}{2006}.
\newblock \bibinfo{title}{Travel information as an instrument to change
  cardrivers’ travel choices: a literature review}.
\newblock \bibinfo{journal}{European Journal of Transport and Infrastructure
  Research} \bibinfo{volume}{6}.
%Type = Techreport
\bibitem[{Dekker et~al.(2018)Dekker, van Lieshout, Ball, Bouman, Dekker,
  Dijkstra, Goverde, Huisman, Panja, Schaafsma et~al.}]{dekker2018next}
\bibinfo{author}{Dekker, M.}, \bibinfo{author}{van Lieshout, R.},
  \bibinfo{author}{Ball, R.}, \bibinfo{author}{Bouman, P.},
  \bibinfo{author}{Dekker, S.}, \bibinfo{author}{Dijkstra, H.},
  \bibinfo{author}{Goverde, R.}, \bibinfo{author}{Huisman, D.},
  \bibinfo{author}{Panja, D.}, \bibinfo{author}{Schaafsma, A.}, et~al.,
  \bibinfo{year}{2018}.
\newblock \bibinfo{title}{A next step in disruption management: Combining
  operations research and complexity science}.
\newblock \bibinfo{type}{Technical Report}.
%Type = Article
\bibitem[{Gao et~al.(2018)Gao, Rasouli, Timmermans and Wang}]{gao2018trip}
\bibinfo{author}{Gao, Y.}, \bibinfo{author}{Rasouli, S.},
  \bibinfo{author}{Timmermans, H.}, \bibinfo{author}{Wang, Y.},
  \bibinfo{year}{2018}.
\newblock \bibinfo{title}{Trip stage satisfaction of public transport users: A
  reference-based model incorporating trip attributes, perceived service
  quality, psychological disposition and difference tolerance}.
\newblock \bibinfo{journal}{Transportation Research Part A: Policy and
  Practice} \bibinfo{volume}{118}, \bibinfo{pages}{759--775}.
%Type = Article
\bibitem[{H{\"o}rl and Balac(2020)}]{horl2020reproducible}
\bibinfo{author}{H{\"o}rl, S.}, \bibinfo{author}{Balac, M.},
  \bibinfo{year}{2020}.
\newblock \bibinfo{title}{Reproducible scenarios for agent-based transport
  simulation: A case study for paris and {\^i}le-de-france} .
%Type = Inproceedings
\bibitem[{Horv{\'a}th and Horv{\'a}th(2015)}]{horvath2015estimation}
\bibinfo{author}{Horv{\'a}th, B.}, \bibinfo{author}{Horv{\'a}th, R.},
  \bibinfo{year}{2015}.
\newblock \bibinfo{title}{Estimation of sample size to forecast travel demand
  in urban public transport}, in: \bibinfo{booktitle}{2015 International
  Conference on Models and Technologies for Intelligent Transportation Systems
  (MT-ITS)}, \bibinfo{organization}{IEEE}. pp. \bibinfo{pages}{300--303}.
%Type = Article
\bibitem[{Kroes and Sheldon(1988)}]{kroes1988stated}
\bibinfo{author}{Kroes, E.P.}, \bibinfo{author}{Sheldon, R.J.},
  \bibinfo{year}{1988}.
\newblock \bibinfo{title}{Stated preference methods: an introduction}.
\newblock \bibinfo{journal}{Journal of transport economics and policy} ,
  \bibinfo{pages}{11--25}.
%Type = Article
\bibitem[{Leng and Corman(2020a)}]{leng2020issue}
\bibinfo{author}{Leng, N.}, \bibinfo{author}{Corman, F.},
  \bibinfo{year}{2020}a.
\newblock \bibinfo{title}{How the issue time of information affects passengers
  in public transport disruptions: an agent-based simulation approach}.
\newblock \bibinfo{journal}{Procedia Computer Science} \bibinfo{volume}{170},
  \bibinfo{pages}{382--389}.
%Type = Article
\bibitem[{Leng and Corman(2020b)}]{leng2020role}
\bibinfo{author}{Leng, N.}, \bibinfo{author}{Corman, F.},
  \bibinfo{year}{2020}b.
\newblock \bibinfo{title}{The role of information availability to passengers in
  public transport disruptions: An agent-based simulation approach}.
\newblock \bibinfo{journal}{Transportation Research Part A: Policy and
  Practice} \bibinfo{volume}{133}, \bibinfo{pages}{214--236}.
%Type = Inproceedings
\bibitem[{Lyons(2006)}]{lyons2006role}
\bibinfo{author}{Lyons, G.}, \bibinfo{year}{2006}.
\newblock \bibinfo{title}{The role of information in decision-making with
  regard to travel}, in: \bibinfo{booktitle}{IEE Proceedings-Intelligent
  Transport Systems}, \bibinfo{organization}{IET}. pp.
  \bibinfo{pages}{199--212}.
%Type = Inproceedings
\bibitem[{Martin et~al.(2016)Martin, Adel{\'e} and
  Reutenauer}]{martin2016strategies}
\bibinfo{author}{Martin, A.}, \bibinfo{author}{Adel{\'e}, S.},
  \bibinfo{author}{Reutenauer, C.}, \bibinfo{year}{2016}.
\newblock \bibinfo{title}{Strat{\'e}gies du voyageur: analyse crois{\'e}e
  d'entretiens semi-directifs}, in: \bibinfo{booktitle}{13{\`e}me Journ{\'e}es
  internationales d'Analyse statistique des Donn{\'e}es Textuelles (JADT
  2016)}.
%Type = Article
\bibitem[{Raimbault and Batty(2021)}]{raimbault2021estimating}
\bibinfo{author}{Raimbault, J.}, \bibinfo{author}{Batty, M.},
  \bibinfo{year}{2021}.
\newblock \bibinfo{title}{Estimating public transport congestion in uk urban
  areas with open transport models} \DOIprefix\doi{10.5281/zenodo.4670012}.
%Type = Article
\bibitem[{Raney et~al.(2003)Raney, Cetin, V{\"o}llmy, Vrtic, Axhausen and
  Nagel}]{raney2003agent}
\bibinfo{author}{Raney, B.}, \bibinfo{author}{Cetin, N.},
  \bibinfo{author}{V{\"o}llmy, A.}, \bibinfo{author}{Vrtic, M.},
  \bibinfo{author}{Axhausen, K.}, \bibinfo{author}{Nagel, K.},
  \bibinfo{year}{2003}.
\newblock \bibinfo{title}{An agent-based microsimulation model of swiss travel:
  First results}.
\newblock \bibinfo{journal}{Networks and Spatial Economics}
  \bibinfo{volume}{3}, \bibinfo{pages}{23--41}.
%Type = Article
\bibitem[{Reuillon et~al.(2013)Reuillon, Leclaire and
  Rey-Coyrehourcq}]{reuillon2013openmole}
\bibinfo{author}{Reuillon, R.}, \bibinfo{author}{Leclaire, M.},
  \bibinfo{author}{Rey-Coyrehourcq, S.}, \bibinfo{year}{2013}.
\newblock \bibinfo{title}{Openmole, a workflow engine specifically tailored for
  the distributed exploration of simulation models}.
\newblock \bibinfo{journal}{Future Generation Computer Systems}
  \bibinfo{volume}{29}, \bibinfo{pages}{1981--1990}.
%Type = Article
\bibitem[{Stamos et~al.(2015)Stamos, Mitsakis, Salanova and
  Aifadopoulou}]{stamos2015impact}
\bibinfo{author}{Stamos, I.}, \bibinfo{author}{Mitsakis, E.},
  \bibinfo{author}{Salanova, J.M.}, \bibinfo{author}{Aifadopoulou, G.},
  \bibinfo{year}{2015}.
\newblock \bibinfo{title}{Impact assessment of extreme weather events on
  transport networks: A data-driven approach}.
\newblock \bibinfo{journal}{Transportation research part D: transport and
  environment} \bibinfo{volume}{34}, \bibinfo{pages}{168--178}.
%Type = Inproceedings
\bibitem[{Tisue and Wilensky(2004)}]{tisue2004netlogo}
\bibinfo{author}{Tisue, S.}, \bibinfo{author}{Wilensky, U.},
  \bibinfo{year}{2004}.
\newblock \bibinfo{title}{Netlogo: A simple environment for modeling
  complexity}, in: \bibinfo{booktitle}{International conference on complex
  systems}, \bibinfo{organization}{Boston, MA}. pp. \bibinfo{pages}{16--21}.

\end{thebibliography}
